Open-Set Domain Adaptation through Self-Supervision

### 2022-02-10 paper/main.tex
Implementation Details Rephrase #1

\subsection{Results}
\label{sec:results}
Table \ref{tab:results} contains the results for all 12 {\bf (ne abbiamo provati davvero 12???)} available domain shifts,
as well as perfomance differences when using multi-head rotation classifiers and center loss.
Further details are to be found in \ref{sec:ablation_study}.
We can notice that multi-headed models are more capable of correctly discriminating between known and unknown samples,
ultimately resulting in better domain alignment.
A further advantage is given when combined with center loss.

\begin{table}
  \centering
  \begin{tabular}[t]{||c|c|c||c|c||}
    \hline
    \multicolumn{5}{||c||}{Single-Head, CE Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Multi-Head, CE Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Single-Head, CE+C Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Multi-Head, CE+C Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline 
    \hline
    \multicolumn{5}{||c||}{No Rotation} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
  \end{tabular}
  \caption{\label{tab:results}Test Caption}
\end{table}

\section{Implementation Details}
\subsection{Model Parameters}
\label{sec:model_parameters}

All models were run using a Stochastic Gradient Descent with batch size 32, a weight decay of 0.0005 and momentum set to 0.9.
For single-headed models, the base learning rate is set to 0.001 and for multi-headed models it is set to 0.003.
This is because multi-headed models take a longer time to converge.
All rotation classifier have the learning rate set to a tenth of the base learning rate.
Learning rates are reduced by a factor of 10 after 90\% of epochs.
All models are run for 50 epochs for the first step described in \ref{eq:sample_separation} and for 25 epochs for the second step described in \ref{sec:domain_alignment}.
For model using the center loss, a centroid learning rate of 0.5 is used.
Other parameters are configuration-sepcific and reported in table \ref{tab:params}.
When considering a "No Rotation" model, it is meant that $\alpha_2 = 0$ is used.

@@

\subsection{Ablation Study}
\label{sec:ablation_study}
As shown by table \ref{tab:results}, different architectures greatly improve performance, and as shown by table \ref{tab:params} each one has its set of optimal parameters.
To choose the best parameters, a sequential approach is followed, by optimizing one parameter at the time.
The order of optimization followed is: $\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
Models not using center loss skip the $\lambda_1$ optimization.
Ablation study were run on two domain shift, Art $\to$ Clipart and Clipart $\to$ Art.
In table \ref{tab:ablation_params} we report the steps followed, picking the parameter that gives the highest mean HOS between the two shifts.
All other settings follow what is reported in \ref{sec:model_parameters}.
For compactness, here are the final results of the data otherwise reported from \ref{tab:ablationoffoff} on.

\begin{table}
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{MH OFF CL OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$  & AUROC & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.5} & \multirow{4}{*}{3.0} & 0.5 & 30\% \\
    3.0 & & & 0.5 & 30\% \\
    5.0 & & & 0.5 & 30\% \\
    10.0 & & & 0.5 & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{4}{*}{1.0} & 0.40 & \multirow{4}{*}{3.0} & 0.5 & 50\%\\
    & 0.50 && 0.5 & 50\% \\
    & 0.55 && 0.5 & 50\% \\
    & 0.60 && 0.5 & 50\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{4}{*}{1.0} & \multirow{4}{*}{0.6} & 1.0 & 0.5 & 50\%\\
    && 3.0 & 0.5 & 50\% \\
    && 5.0 & 0.5 & 50\% \\
    && 10.0 & 0.5 & 50\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Final Parameters} \\
    \hline
    1.0 & 0.6 & 3.0 & 0.5 & 50\%\\
    \hline
  \end{tabular}
  \caption{\label{tab:ablationoffoff} Ablation performed for OFF-OFF configuration}
\end{table}
\section{Future Work}

>>>>

\subsection{Results}
\label{sec:results}
Table \ref{tab:results} contains the results for all 12 {\bf (ne abbiamo provati davvero 12???)} available domain shifts,
as well as perfomance differences when using multi-head rotation classifiers and center loss.
Further details are to be found in section \ref{sec:implementation_details}.
We can notice that multi-headed models are more capable of correctly discriminating between known and unknown samples,
ultimately resulting in better domain alignment.
A further advantage is given when combined with center loss.
AUROC values are computed at the end of the separation stage, 
while HOS values are sampled at regular times on the entire original target dataset.

\begin{table}
  \centering
  \begin{tabular}[t]{||c|c|c||c|c||}
    \hline
    \multicolumn{5}{||c||}{Single-Head, CE Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Multi-Head, CE Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Single-Head, CE+C Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Multi-Head, CE+C Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline 
    \hline
    \multicolumn{5}{||c||}{No Rotation} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Results for domain alignment. AUROC is the area under the ROC. HOS is latest achieved HOS, HOS* the best achieved through all epochs.}
\end{table}

\section{Implementation Details}
\label{sec:implementation_details}
\subsection{Model Parameters}
\label{sec:model_parameters}

All models were run using stochastic gradient descent with batch size 32,
a weight decay of 0.0005 and momentum of 0.9.
For single-headed models, 
a base learning rate of 0.001 is used,
while for multi-headed models it is set to 0.003.
This is because only one head of the heads is trained with each samples,
so the process needs to be sped up.
Rotation classifier use a learning rate set to a tenth of the base learning rate.
A step learning rate scheduler is used, reducing it by a factor of 10 after 90\% of epochs.
All models are run for 50 epochs for the first step described in \ref{eq:sample_separation} and for 25 epochs for the second step described in \ref{sec:domain_alignment}.
For model using the center loss a centroid learning rate of 0.5 is used.
All other parameters are configuration-sepcific and are reported in table \ref{tab:params}.
"No Rotation" model is the same as a single-head without center loss model with $\alpha_2 = 0$.

% % %

{\it Extractor E}: The extractor employed is a ResNet-34{\bf[Inserire cit a ResNet]} {\bf è pretrained???} {\bf ma 34 o 18???} for all classifiers.

{\it Classifier $C_1$, $C_2$}: $C_1$ is composed of a 45 dimensional output. 
All unknown samples are mapped as belonging to class 45.
$C_1$ is used as a starting point for $C_2$.
As no unknowns are present on the source dataset (they are removed),
the weight of unknwon samples in the second step is set to {\bf spiegare come è bilanciato} while for all other classes it is set to 1.
A single fully connected layer $512\to 45$ with batch-norm is used.

{\it Classifier $R_1$, $R_2$}: 
$R_1$ and $R_2$ are composed by a $1024\to 256$  and a $256\to 4$ fully connected layers, named {\it Discriminators}.
The 256-dimensional output are the features used by the center loss for inferring class centers.
If multi-head is used, each head is a separate discriminator.
$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.

@@

\subsection{Ablation Study}
\label{sec:ablation_study}
As shown in table \ref{tab:results} different architectures give different results, 
and as shown in table \ref{tab:params} each one requires a different set of parameters.
To choose optimal parameters a sequential approach is followed, 
by optimizing one parameter at the time.
The order of optimization followed is: 
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run on two domain shifts, 
Art $\to$ Clipart and Clipart $\to$ Product.
In table \ref{tab:ablation_params} we report the steps followed.
All other settings follow what is reported in \ref{sec:model_parameters}.
The result here obtained are the same reported in table \ref{tab:params}.

\begin{table}
  \centering
  \begin{tabular}[h]{||c|c|c||c|c||}
    \hline
    \multicolumn{5}{||c||}{MH OFF CL OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$  & AUROC & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.5} & \multirow{4}{*}{3.0} & 0.5 & 30\% \\
    3.0 & & & 0.5 & 30\% \\
    5.0 & & & 0.5 & 30\% \\
    10.0 & & & 0.5 & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{4}{*}{1.0} & 0.40 & \multirow{4}{*}{3.0} & 0.5 & 50\%\\
    & 0.50 && 0.5 & 50\% \\
    & 0.55 && 0.5 & 50\% \\
    & 0.60 && 0.5 & 50\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{4}{*}{1.0} & \multirow{4}{*}{0.6} & 1.0 & 0.5 & 50\%\\
    && 3.0 & 0.5 & 50\% \\
    && 5.0 & 0.5 & 50\% \\
    && 10.0 & 0.5 & 50\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Final Parameters} \\
    \hline
    1.0 & 0.6 & 3.0 & 0.5 & 50\%\\
    \hline
  \end{tabular}
  \caption{\label{tab:ablationoffoff} Ablation performed for OFF-OFF configuration}
\end{table}
\section{Future Work}
